|

### 2025-05-05 doc/paper.qmd
Structure Aligned with Accounting Chair Requieremnts

---
format:
  pdf:
    documentclass: article
    number-sections: true
    toc: true
    lof: true
    lot: true
    include-before-body:
      - titlepage.tex
      - acknowledgements.tex
      - abstract.tex
      - abbreviations.tex
    include-after-body:
      - declaration.tex

@@

fig_caption: yes
fontsize: 11pt
ident: yes
always_allow_html: yes
number-sections: true
header-includes:
  - \usepackage[nolists]{endfloat}
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption}
  - \captionsetup[table]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage{indentfirst}
  - \usepackage[margin=1in]{geometry}
---

@@

\pagenumbering{arabic}

@@

\setcounter{table}{0}
\renewcommand{\thetable}{\arabic{table}}

>>>>

---
format:
  pdf:
    documentclass: article
    number-sections: true
    toc: true
    lof: true
    lot: true
    include-before-body:
      - titlepage.tex
      - preamble.tex  # This sets Roman page numbering before the TOC
    include-after-body:
      - declaration.tex

@@

fig_caption: yes
fontsize: 12pt
ident: yes
always_allow_html: yes
number-sections: true
header-includes:
  - \usepackage[nolists]{endfloat}
  - \usepackage{setspace}\onehalfspacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption}
  - \captionsetup[table]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage{indentfirst}
  - \usepackage[margin=1in]{geometry}
  - \usepackage{ragged2e} #for declaration intend
---

@@

\clearpage
# Acknowledgements {-}
I would like to thank my professors, colleagues, and friends for their support and insights throughout the preparation of this thesis. Special thanks go to [Name], whose guidance was invaluable during the project.

\clearpage

# Abstract {-}
This thesis examines how much new information is conveyed in quarterly earnings announcements, replicating and extending the study by Ball and Shivakumar (2008). Using a reproducible workflow based on the TRR 266 Template, I analyze U.S. and Canadian data from 1972 to 2023, applying an event-study design to assess the explanatory power of earnings windows on annual stock returns. The findings show that earnings informativeness varies across time and jurisdictions, with evidence suggesting institutional factors influence market reactions. A non-archival survey design is also proposed to explore investor perceptions, enriching the archival analysis with complementary behavioral insights.

\newpage

# List of Abbreviations {-}
\setlength{\parindent}{0em}
**BHR**: Buy-and-Hold Returns   
**CRSP**: Center for Research in Security Prices  
**DS**: Datastream  
**IDE**: Integrated Development Environment  
**TREAT**: TRR 266 Template for Reproducible Empirical Accounting Research  
**WRDS**: Wharton Research Data Services  
**WSCP**: Worldscope

\newpage
\pagenumbering{arabic}
\setlength{\parindent}{4em}
\setlength{\parskip}{0em}
\newgeometry{left=6cm, right=1.5cm, top=2cm, bottom=2cm}

@@

\restoregeometry
\setcounter{table}{0}
\renewcommand{\thetable}{\arabic{table}}
